Staged Abstract Interpreters

### 2019-09-08 paper/20_prelim.tex
typo

The abstract syntax we present can be seen as a deep embedding of the
language -- we use data-types to represent programs. This design choice allows us
to use different interpretations over the AST; with the inheritance and
overriding mechanisms in Scala, we may also add new language constructs and reuse
existing interpretations.

@@

A monad is a type constructor @M[_]: * --> *@ with two operations, often called
@return@ and @bind@. Informally, @return@ wraps a value into a monad @M@, and
@bind@ unwraps a monadic value and transforms it into a new monadic value.
Pragmatically in Scala, we define the monad type class using trait @Monad@ (Figure
\ref{fig:monad}), which it declares the @pure@ \footnote{We elect to use
\texttt{pure} as the name, since \texttt{return} is a keyword in Scala and
\texttt{unit} is a built-in function in LMS.} and @flatMap@ operation. The trait
itself takes the monad type constructor @M[_]@ as an argument, which, as a
higher-kinded type, takes a type and returns a type. The method @pure@
promotes values of type @A@ to values of type @M[A]@. The monadic @bind@
operation is usually called @flatMap@ in Scala. It takes a
monad-encapsulated value of type @M[A]@, a function of @A => M[B]@ and returns
values of type @M[B]@.

>>>>

The abstract syntax we present can be seen as a deep embedding of the language:
we use data-types to represent programs. This design choice allows us to use
different interpretations over the AST; with the inheritance and overriding
mechanisms in Scala, we may also add new language constructs and reuse existing
interpretations.

@@

A monad is a type constructor @M[_]: * --> *@ with two operations, often called
@return@ and @bind@. Informally, @return@ wraps a value into a monad @M@, and
@bind@ unwraps a monadic value and transforms it into a new monadic value.
Pragmatically in Scala, we define the monad type class using trait @Monad@
(Figure \ref{fig:monad}), which declares the @pure@ \footnote{We elect to use
\texttt{pure} as the name, since \texttt{return} is a keyword in Scala and
\texttt{unit} is a built-in function in LMS.} and @flatMap@ operations. The
trait itself takes the monad type constructor @M[_]@ as an argument, which, as a
higher-kinded type, takes a type and returns a type. The method @pure@ promotes
values of type @A@ to values of type @M[A]@. The monadic @bind@ operation is
usually called @flatMap@ in Scala. It takes a monad-encapsulated value of type
@M[A]@, a function of @A => M[B]@, and returns values of type @M[B]@.
